Including EW and mixed QCD-EW corrections into PDF fits

### 2020-04-06 paper/paper.tex
Small tweak
adding plots using pgf

\usepackage{jheppub}
\usepackage[T1]{fontenc}

@@

\begin{table}
    \centering
    \begin{tabular}{l|c|cc}
        \multicolumn{1}{l}{} &  & \multicolumn{2}{c}{$\chi^{2}/n_{{\rm data}}$}\tabularnewline
        \hline
        Dataset & $n_{{\rm data}}$ & QCD & QCD+EW\tabularnewline
        \hline
        ATLAS HM DY 7 TeV & 13 & 1.151 & 1.036\tabularnewline
        \hline
        ATLAS $\sigma_{tt}^{{\rm tot}}$ & 3 & 2.549 & 3.271\tabularnewline
        \hline
        CMS $\sigma_{tt}^{{\rm tot}}$ & 3 & 0.986 & 1.654\tabularnewline
        \hline
    \end{tabular}
    \caption{$\chi^2$ values for NNPDF3.1 NLO luxQED.}
    \label{table:chi2}
\end{table}

\begin{figure}
    \includegraphics[width=0.5\textwidth]{plots/matched_datasets_from_dataspecs0_plot_fancy_dataspecs_0}
    \includegraphics[width=0.5\textwidth]{plots/matched_datasets_from_dataspecs0_datanorm_plot_fancy_dataspecs_0}
    \includegraphics[width=0.5\textwidth]{plots/matched_datasets_from_dataspecs1_plot_fancy_dataspecs_0}
    \includegraphics[width=0.5\textwidth]{plots/matched_datasets_from_dataspecs1_datanorm_plot_fancy_dataspecs_0}
    \includegraphics[width=0.5\textwidth]{plots/matched_datasets_from_dataspecs2_plot_fancy_dataspecs_0}
    \includegraphics[width=0.5\textwidth]{plots/matched_datasets_from_dataspecs2_datanorm_plot_fancy_dataspecs_0}
    \caption{Data prediction comparison plots.}
    \label{fig:datacomparison}
\end{figure}

>>>>

\usepackage{jheppub}
\usepackage[T1]{fontenc}
\usepackage{pgf}

@@

\begin{table}
    \centering
    \begin{tabular}{l|c|c}
        \hline
        Dataset & $n_{{\rm data}}$ & $\chi^{2}/n_{{\rm data}}$ \tabularnewline
        \hline
        ATLAS HM DY 7 TeV & 13 & 1.39 \tabularnewline
        \hline
        CMS $\sigma_{tt}^{{\rm tot}}$ & 3 & 1.78\tabularnewline
        \hline
    \end{tabular}
    \caption{$\chi^2$ values for NNPDF3.1 NLO luxQED.}
    \label{table:chi2}
\end{table}

\begin{figure}
    \resizebox{0.5\textwidth}{!}{\input{plots/ATLASZHIGHMASS49FB.pgf}}
    \resizebox{0.5\textwidth}{!}{\input{plots/CMSTTBARTOT.pgf}}
    \caption{Data prediction comparison plots.}
    \label{fig:datacomparison}
\end{figure}
